\cvsection{Research Experience}
% \cvsubsection{Research}
\begin{cventries}

  \cventry
    {\href{https://idiap.ch}{Idiap Research Institute}}
    {Graduate Research Assistant}
    {EPFL}
    {May. 2019 - Present}
    {
      Working on project \href{http://www.idiap.ch/project/dusk2dawn/}{Dusk2Dawn}, a multidisciplinary research project that using rich data gathered by young volunteers using smartphones aims to provide answers to a number of important questions related to the night behavior of young Swiss people. 
    }

  \cventry
    {\href{https://www.c3sr.com/participants/}{IBM-Illinois Center for Cognitive Computing Systems Research}}
    {Research Affiliate}
    {University of Illinois at Urbana-Champaign}
    {Sept. 2018 - May 2019}
    {
      Worked on project \href{http://listen.online}{listen.online}, a user-based social channel search engine, where people can find social channels from different sources, such as Reddit, Twitter, YouTube, etc, based on the attributes of the contributing users. %Under supervision of Prof. Kevin Chen-Chuan Chang.
    }
    
  \cventry
    {\href{https://www.linkedin.com/company/sharif-ict-innovation-center/}{Sharif ICT Innovation Center}}
    {Research Assistant}
    {Sharif University of Technology}
    {Sept. 2016 - May 2019}
    {
      Worked on analysis and mining of big data from the web and social media, in applications ranging from online social networks to health-related products.
      %Under supervision of Prof. Hamid R. Rabiee.
    }
    
  \cventry
    {\href{http://dml.ce.sharif.edu/dmlsite/?q=people}{Data Science and Machine Learning Lab}}
    {Research Assistant}
    {Sharif University of Technology}
    {Dec. 2014 - Sept. 2016}
    {
      Worked on cross-platform social network analysis and mining, specifically link prediction in multi-layer heterogeneous social networks.
      %Under supervision of Prof. Hamid R. Rabiee.
    }
\end{cventries}

    
\cvsection{Teaching Experience
% \footnote{TA roles that have been undertaken as an undergraduate student are omitted due to space limit.}
}
\begin{cventries}
\cventry
    {Department of Computer Engineering}
    {Adjunct Lecturer}
    {Sharif University of Technology}
    {Fall 2017}
    {\href{http://ce.sharif.edu/courses/96-97/1/ce153-12/}{Fundamentals of Programming (Python)}
    }
    
\cvexptitle{Graduate Teaching Assistant}{Sharif University of Technology}
\cvexppos{Spring 2017}{Artificial Intelligence, by Dr. Mahdieh Soleymani}
\cvexppos
    {Spring 2016}
    {
      Statistical Learning Theory (Advanced Topics in Artificial Intelligence), by Prof. Hamid R. Rabiee
    }
\cvexppos
    {Spring 2016}
    {
      Engineering Probability and Statistics, by Prof. Hamid R. Rabiee and SeyedAbbas Hosseini
    }
    
\cvexptitle{Teaching Assistant}{University of Isfahan}
\cvexppos
    {Fall 2013}
    {
      Artificial Intelligence, by Dr. Amirhassan Monadjemi
    }
\cvexppos
    {Fall 2012}
    {
      Advanced Computer Programming 2 (Java), by Dr. Ahmad Zaeri
    }
\cvexppos
    {Fall 2011}
    {
      Computer Programming (Java), by Dr. Bahman Zamani
    }
\cvexppos
    {Fall 2011}
    {
      Computer Programming (C++), by Dr. Bijan Shoushtarian
    }
    
\cventry
    {Project: Design and Implementation of Honeypot Websites to Detect Potential Fraud in Bulk Web Traffic Providers}
    {Mentorship}
    {Sharif University of Technology}
    {Fall 2016 -- Fall 2017}
    {Soheil Sheybani, BSc Student, Department of Computer Engineering}
    
\end{cventries}

\cvsection{Professional Experience}
\begin{cventries}
\cventry
    {Sharif ICT Innovation Center}
    {Big-Data Engineer}
    {Tehran, Iran}
    {Sept. 2018 - May 2019}
    {
      Responsible for building a native big-data processing platform using state of the art technologies, such as Spark, Cassandra, JanusGraph, Elasticsearch, etc.
    }
\cventry
    {Amin Computer Co.}
    {Software Engineer}
    {Isfahan, Iran}
    {Summer 2012}
    {
      Responsible for designing and developing a mobile application for company's web-based human resource management system.
    }
  \cventry
    {Faculty of Engineering, University of Isfahan}
    {Web Developer}
    {Isfahan, Iran}
    {Nov. 2010 - May. 2011}
    {
      Responsible for developing and maintaining the website of the 3rd Iranian Conference on Renewable Energies and Distributed Generation.
    }
\end{cventries}

% \cvsection{Mentorship}
% \begin{cventries}
% \cventry
%     {BSc Student, Department of Computer Engineering}
%     {\href{http://ce.sharif.ir/~sheybani}{Soheil Sheybani}}
%     {Sharif University of Technology}
%     {Fall 2016 -- Fall 2017}
%     {
%     Project: Design and Implementation of Honeypot Websites to Detect Potential Fraud in Bulk Web Traffic Providers
%     }
% \end{cventries}
